---
title: "Cassie GLMM"
documentclass: article
classoption: a4paper
output: word_document
fig_height: 50%
fig_width: 50%
geometry: margin=0.787in
---

# Cassie Bond - Generalised Linear Mixed Models for microplastics data

```{r read data if needed, eval=FALSE, include=FALSE, paged.print=FALSE}
setwd("C:/Users/00028958/LocalData/R Projects/Cassie_Bond/")
cassie <- read.csv("cassie.csv" , stringsAsFactors = T)
summary(cassie)
str(cassie)
```

```{r load packages etc, echo=-1, paged.print=FALSE}
load("C:/Users/00028958/LocalData/R Projects/Cassie_Bond/.Rdata")
library(nlme)
library(multcomp)
library(car)
```

### within each of the catchments - run t test

to see whether there is a difference between the catchments or sites

```{r}
cat("_______________ Comparisons by Drain (Catchment) _______________\n")
meanz <- signif(tapply(cassie$count_corr_across_sizes.L, cassie$Drain, mean),3)
sdz <- signif(tapply(cassie$count_corr_across_sizes.L, cassie$Drain, sd),3)
rsdz <- signif(100*sdz/meanz,3); rbind(meanz,sdz, rsdz)
with(cassie, oneway.test(count_corr_across_sizes.L ~ Drain))
with(cassie, pairwise.t.test(count_corr_across_sizes.L, Drain, p.adjust.method = "none", pool.sd = F))
with(cassie, kruskal.test(count_corr_across_sizes.L ~ Drain))
cat("\n_______________________ Comparisons by Site _______________________\n")
meanz <- signif(tapply(cassie$count_corr_across_sizes.L, cassie$Site, mean),3)
sdz <- signif(tapply(cassie$count_corr_across_sizes.L, cassie$Site, sd),3)
rsdz <- signif(100*sdz/meanz,3); rbind(meanz,sdz, rsdz)
with(cassie, oneway.test(count_corr_across_sizes.L ~ Site))
with(cassie, pairwise.t.test(count_corr_across_sizes.L, Site, p.adjust.method = "none", pool.sd = F))
with(cassie, kruskal.test(count_corr_across_sizes.L ~ Site))
```

We see here that *there is no difference in microplastic concentrations between Drains or Sites*.

We should check if the two sites in each drain have significantly different counts:

```{r within drain comps, paged.print=F}
cat("Welch t-tests comparing 2 sites in each drain separately:\n\n")
for (i in 1:nlevels(cassie$Drain)){
  tt0 <- with(droplevels(subset(cassie, cassie$Drain==levels(cassie$Drain)[i])), 
     t.test(count_corr_across_sizes.L ~ Site))
  n1 <- substr(names(tt0$estimate[1]),nchar(names(tt0$estimate)[1])-2,
               nchar(names(tt0$estimate)[1]))
  n2 <- substr(names(tt0$estimate[2]),nchar(names(tt0$estimate)[2])-2,
               nchar(names(tt0$estimate)[2]))
  cat("Sites in drain",levels(cassie$Drain)[i],
      ": p = ",signif(tt0$p.value,3),"; mean",n1,"=",signif(tt0$estimate[1],3),
      ", mean",n2,"=",signif(tt0$estimate[2],3),"\n")
}
rm(list = c("tt0","n1","n2"))
```

So all within-drain comparisons show no significant difference in mean $\mu$plastic counts.

*There is no difference between Drains or Sites, or between sites within drains.*

<hr>

# Variance decomposition (Type-II ANOVA model)

## one level decomposition

```{r one level variance decomposition}
one.level <- lme(count_corr_across_sizes.L ~ 1, 
                 random = ~1|Drain, data = cassie) 
VarCorr(one.level)
# rough check
7/57
```

Overall, drains don't explain the variation (12%)

## Two level decomposition

A two level decomposition maybe makes more sense, so lets do that properly

```{r two level variance decomposition}
two.level <- lme(count_corr_across_sizes.L ~ 1, random = ~1|Drain/Site, data = cassie) 
VarCorr(two.level)
var.out <- VarCorr(two.level)
drains <- as.numeric(var.out[2,1])
site <- as.numeric(var.out[4,1])
within.site <- as.numeric(var.out[5,1])
tot <- drains + site + within.site; cat("\n")
drains/tot
site/tot
within.site/tot
```

-   3% variation at the drain level
-   23% variation by site, unrelated to drain
-   73% variation residual:

I think this converts to a "plastic is ubiquitous" story; neither site nor drain explains the variation.

<hr>

# AnOVa model treating Drain as a factor

```{r anova by Drain, paged.print=FALSE}
lme.a <- lme(log(count_corr_across_sizes.L) ~
               Drain,
             random = ~1|Site, data = cassie)  
summary(lme.a)
Anova(lme.a)
```

# allow for unequal group variance at the drain level

```{r anova by Drain unequal variance, paged.print=FALSE}
lme.b <- lme(log(count_corr_across_sizes.L) ~
               Drain, weights = varIdent(form = ~1 | Drain),
             random = ~1|Site, data = cassie)  
summary(lme.b)
anova(lme.b,lme.a)
```

*Allowing for heterogeneous variance is not a statistically significant improvement*

So model b is over fitting, and then with over fitting we get a difference...

... but just to see what happens

```{r Tukey pairwise, paged.print=FALSE}
Anova(lme.b)
Anova(lme.a)

Tukey.b <- glht(lme.b, linfct = mcp(Drain = "Tukey"))
summary(Tukey.b)

Tukey.a <- glht(lme.a, linfct = mcp(Drain = "Tukey"))
summary(Tukey.a)
```

# slightly different variance structure

```{r slightly diff variance structure, paged.print=FALSE}
lme.c <- lme(log(count_corr_across_sizes.L) ~
               Drain, weights = varIdent(form = ~1 | Site),
             random = ~1|Site, data = cassie)  
summary(lme.c)
cat("\nAnOVa to compare models\n");  anova(lme.c,lme.a)

Tukey.c <- glht(lme.c, linfct = mcp(Drain = "Tukey"))
summary(Tukey.c)
```

Maybe there is something about drain K, but also this is over fitting

**Lets not chase p-values! that would be bad science**

There is no additional variance structure assumption needed. *No different across drains*.

<hr>

*Now explore regression model options for covariates that might make sense*.

# REGRESSION on CATCHMENT POPULATION

## MP on population, ungrouped

```{r overall effect of catchment population, paged.print=FALSE}
ctrl <- lmeControl(opt='optim')  # less flakey search strategy
ctrl <- lmeControl(opt='optim',   # default is 50: it will
                   maxIter=1000)  # run for a while if you crank it up

cassie$pop <- cassie$catchment_pop/1e3

lme.base <- lme(count_corr_across_sizes.L ~ pop, 
                control = ctrl,
                random = ~1|Site, 
                data = cassie)  
summary(lme.base)
```

There is no overall effect but this may be because the variation differs between Drain or Site groups:

## MP on Population varying by Drain

```{r by population AND catchment, paged.print=FALSE}
lme.base.het1 <- lme(count_corr_across_sizes.L ~ pop, 
                     weights = varIdent(form = ~1 | Drain), 
                     control = ctrl,
                     random = ~1|Site, 
                     data = cassie)  
summary(lme.base.het1)

cat("\nAnOVa to compare models\n");  anova(lme.base,lme.base.het1)
```

The anova shows a low p-value, meaning the heterogeneous model *population by Drain* has a better fit.

## MP on Population varying by Site

```{r by population AND site, paged.print=FALSE}
lme.base.het2 <- lme(count_corr_across_sizes.L ~ pop, 
                     weights = varIdent(form = ~1 | Site), 
                     control = ctrl,
                     random = ~1|Site, 
                     data = cassie)  
summary(lme.base.het2)
cat("\nAnOVa to compare models\n");  anova(lme.base,lme.base.het1,lme.base.het2)
```

Heterogeneous 2 model (by Site) is a stat better fit that heterogeneous 1 model (by Drain): variation at site level catchment **population** is statistically significant. *This can be treated as an empirical question*.

<hr>

# REGRESSION on CATCHMENT AREA

## MP on area, ungrouped

```{r basic regression on area, paged.print=FALSE}
lme.base <- lme(count_corr_across_sizes.L ~ catchment_area, 
                control = ctrl,
                random = ~1|Site, 
                data = cassie)  
summary(lme.base)
```

There does seem to be an *effect of catchment area (p < 0.05)*...<br> ...so we test if there's a better fit if we separate the effect of Drain:

## MP on area varying by Drain

```{r regression on area by Drain, paged.print=FALSE}
lme.base.het1 <- lme(count_corr_across_sizes.L ~ catchment_area, 
                     weights = varIdent(form = ~1 | Drain), 
                     control = ctrl,
                     random = ~1|Site, 
                     data = cassie)  
summary(lme.base.het1)

cat("\nAnOVa to compare models\n");  anova(lme.base,lme.base.het1)
```

The anova shows a low p-value, meaning the heterogeneous model *catchment area by Drain* has a better fit.

## MP on area varying by Site

```{r by catchment area AND site, paged.print=FALSE}
lme.base.het2 <- lme(count_corr_across_sizes.L ~ catchment_area, 
                     weights = varIdent(form = ~1 | Site), 
                     control = ctrl,
                     random = ~1|Site, 
                     data = cassie)  
summary(lme.base.het2)
cat("\nAnOVa to compare models\n");  anova(lme.base,lme.base.het1,lme.base.het2)
```

Heterogeneous 2 model (by Site) is a stat better fit that heterogeneous 1 model (by Drain): variation at site level catchment **area** is statistically significant.

<hr>

# REGRESSION on RAINFALL

## MP on rainfall, ungrouped

```{r basic regression on preceding rainfall, paged.print=FALSE}
lme.base <- lme(count_corr_across_sizes.L ~
                  rainfall, control = ctrl,
                random = ~1|Site, data = cassie)  
summary(lme.base)
```

So overall preceding rainfall has no effect, but what if we split the data by Drain ...

## MP on rainfall varying by Drain

```{r MP on rainfall by Drain, paged.print=FALSE}
lme.base.het1 <- lme(count_corr_across_sizes.L ~ rainfall, 
                     weights = varIdent(form = ~1 | Drain), 
                     control = ctrl,
                     random = ~1|Site, 
                     data = cassie)  
summary(lme.base.het1)
cat("\nANOVA to compare models\n"); anova(lme.base,lme.base.het1)
```

AIC and low p-value mean that the heterogeneous model (by Drain) is a better fit, but **no significant effect of rainfall**.

## MP on rainfall varying by Site

```{r MP on rainfal by Site, paged.print=FALSE}
lme.base.het2 <- lme(count_corr_across_sizes.L ~ rainfall, 
                     weights = varIdent(form = ~1 | Site), 
                     control = ctrl,
                     random = ~1|Site, 
                     data = cassie)  
summary(lme.base.het2)
cat("\nANOVA to compare models\n"); anova(lme.base,lme.base.het1,lme.base.het2)
```

Based on AIC and p-values, heterogeneous 2 model (by Site) is a statistically better fit that heterogeneous 1 model (by Drain): *BUT* variation from **rainfall is not statistically significant**.

The variance decomposition (*at the beginning*) possibly means that, at site level, variance makes sense; this can be treated as an empirical question

<hr>

Exploration of log(Y) is something you can look at. [**Note**: anova() can't be used to compare models explaining log(Y) with models explaining Y] 

```{r log MP vs rainfall and Site, paged.print=FALSE}
lme.base.het2.log <- lme(log(count_corr_across_sizes.L) ~
                           rainfall, 
                         weights = varIdent(form = ~1 | Site), 
                         control = ctrl,
                         random = ~1|Site, 
                         data = cassie)  
summary(lme.base.het2.log)
```

So using log(rainfall) still doesn't let us see a significant effect of rainfall

### Looking for nonlinear effect with quadratic of rainfall


```{r quadratic rainfall Site, paged.print=FALSE}
lme.base.het2.quad <- lme(count_corr_across_sizes.L ~ rainfall + I(rainfall^2),
                          weights = varIdent(form = ~1 | Site), 
                          control = ctrl,
                          random = ~1|Site, 
                          data = cassie)
summary(lme.base.het2.quad)
```

nothing here...

let's scale up..

```{r scale up quadratic rain and Site, paged.print=FALSE}
cassie$rain <-cassie$rainfall/1000

lme.base.het2.quad2 <- lme(count_corr_across_sizes.L ~ rain + I(rain^2), 
                           weights = varIdent(form = ~1 | Site), 
                           control = ctrl,
                           random = ~1|Site, 
                           data = cassie)  
summary(lme.base.het2.quad2)
```

Still no effect of rainfall

###  maybe impose cubic

```{r cubic of rainfall plus vary by Site, paged.print=FALSE}
lme.base.het2.cub <- 
  lme(count_corr_across_sizes.L ~ I(rainfall^3), 
      weights = varIdent(form = ~1 | Site), 
      control = ctrl,
      random = ~1|Site, 
      data = cassie)  
summary(lme.base.het2.cub)
```

Still no effect of rainfall

```{r summary of quad model, paged.print=F}
summary(lme.base.het2.quad2)
```

###  log x would capture this, approximately

```{r try log rainfall, paged.print=F}
lme.base.het2.xlog <- lme(count_corr_across_sizes.L ~ log(rainfall), 
                          weights = varIdent(form = ~1 | Site), 
                          control = ctrl,
                          random = ~1|Site, 
                          data = cassie)  
summary(lme.base.het2.xlog)
```

**None of the options show a significant effect of prior rainfall**

<hr>

# REGRESSION on RESIDENTIAL PROPORTION

## MP on residential, ungrouped

```{r basic model, paged.print=FALSE}
lme.base <- lme(count_corr_across_sizes.L ~ residential, 
                control = ctrl,
                random = ~1|Site, 
                data = cassie)  
summary(lme.base)
```

No ungrouped effect of proportion of residential land in catchments...

## MP on Residential varying by Drain

```{r MP on residential and Drain, paged.print=F}
lme.base.het1 <- lme(count_corr_across_sizes.L ~ residential, 
                     weights = varIdent(form = ~1 | Drain), 
                     control = ctrl,
                     random = ~1|Site, 
                     data = cassie)  
summary(lme.base.het1)
cat("\nAnOVa to compare models\n"); anova(lme.base,lme.base.het1)
```

Lower AIC and p<0.05 mean heterogeneous model (by Drain) is a better fit...

## MP on residential varying by Site

```{r residential varying by site, paged.print=F}
lme.base.het2 <- lme(count_corr_across_sizes.L ~
                       residential, weights = varIdent(form = ~1 | Site), control = ctrl,
                     random = ~1|Site, data = cassie)  
summary(lme.base.het2)
cat("\nAnOVa to compare models\n"); anova(lme.base,lme.base.het1,lme.base.het2)
```

So heterogeneous 1 model (by Drain) is a statistically better fit than heterogeneous 2 model (by Site) = variation at *catchment* level.

**Residential proportion** is statistically significant - *negative* relationship.

<hr>

# REGRESSION on AGRICULTURAL PROPORTION

## Ungrouped model -- MP by agricultural

```{r MP on agric ungrouped, paged.print=FALSE}
lme.base <- lme(count_corr_across_sizes.L ~ agricultural, 
                control = ctrl,
                random = ~1|Site, 
                data = cassie)  
summary(lme.base)
```

So in an ungrouped model the proportion of agricultural land is not significant.

## MP on agric and Drain

```{r MP on agric and Drain, paged.print=FALSE}
lme.base.het1 <- lme(count_corr_across_sizes.L ~ agricultural,
                     weights = varIdent(form = ~1 | Drain), 
                     control = ctrl,
                     random = ~1|Site, 
                     data = cassie)  
summary(lme.base.het1)
cat("\nAnOVa to compare models\n"); anova(lme.base,lme.base.het1)
```

Low AIC and p-value say heterogeneous model a better fit, but agricultural proportion still shows no significant effect.

```{r MP on agric and Site, paged.print=FALSE}
lme.base.het2 <- lme(count_corr_across_sizes.L ~ agricultural, 
                     weights = varIdent(form = ~1 | Site), 
                     control = ctrl,
                     random = ~1|Site, 
                     data = cassie)  
summary(lme.base.het2)
cat("\nAnOVa to compare models\n");  anova(lme.base,lme.base.het1,lme.base.het2)
```

heterogeneous 2 model is a stat better fit that heterogeneous 1 model: variation at site level

**Agricultural proportion is still not stat significant**.

##  exploration of log(agricultural) 

```{r log agric, paged.print=FALSE}
lme.base.het2.log <- lme(log(count_corr_across_sizes.L) ~ agricultural, 
                         weights = varIdent(form = ~1 | Site), 
                         control = ctrl,
                         random = ~1|Site, 
                         data = cassie)  
summary(lme.base.het2.log)
```

###  Looking for nonlinear effect

```{r quad agric, paged.print=FALSE}
lme.base.het2.quad <- 
  lme(count_corr_across_sizes.L ~ agricultural + I(agricultural^2), 
      weights = varIdent(form = ~1 | Site), 
      control = ctrl,
      random = ~1|Site, 
      data = cassie)  
summary(lme.base.het2.quad)
```

maybe something here:  hard to see

### so lets scale so we can see what is happening

```{r agric upscaled quad, paged.print=FALSE}
cassie$ag <-cassie$agricultural/1000

lme.base.het2.quad2 <- 
  lme(count_corr_across_sizes.L ~ ag + I(ag^2), 
      weights = varIdent(form = ~1 | Site), 
      control = ctrl,
      random = ~1|Site, 
      data = cassie)  
summary(lme.base.het2.quad2)
```

###  maybe impose cubic

```{r cubic agric, paged.print=FALSE}
lme.base.het2.cub <- 
  lme(count_corr_across_sizes.L ~ I(agricultural^3), 
      weights = varIdent(form = ~1 | Site), 
      control = ctrl,
      random = ~1|Site, 
      data = cassie)  
summary(lme.base.het2.cub)
```

Not cubic <br>
so look closely at the quadratic maybe runs the other way

```{r summary quad, paged.print=F}
summary(lme.base.het2.quad2)
```

**None of the options show a significant effect of the proportion of agricultural land in each catchment**

<hr>

# REGRESSION on INDUSTRIAL PROPORTION

## MP on proportion industrial -- ungrouped

```{r MP on industrial, paged.print=F}
lme.base <- lme(count_corr_across_sizes.L ~ industrial, 
                control = ctrl,
                random = ~1|Site, 
                data = cassie)  
summary(lme.base)
```

So, no ungrouped effect of industrial land proportion.

## MP on Proportion industrial varying by Drain

```{r MP on Proportion industrial varying by Drain, paged.print=FALSE}
lme.base.het1 <- lme(count_corr_across_sizes.L ~ industrial, 
                     weights = varIdent(form = ~1 | Drain), 
                     control = ctrl,
                     random = ~1|Site, 
                     data = cassie)  
summary(lme.base.het1)
cat("\nAnOVa to compare models\n");  anova(lme.base,lme.base.het1)
```


So, no effect of industrial land proportion grouped by Drain, but low AIC and p-value < 0.05 mean heterogeneous model is a better fit.

## MP on Proportion industrial varying by Site

```{r MP on Proportion industrial varying by Site, paged.print=F}
lme.base.het2 <- lme(count_corr_across_sizes.L ~ industrial, 
                     weights = varIdent(form = ~1 | Site), 
                     control = ctrl,
                     random = ~1|Site,
                     data = cassie)  
summary(lme.base.het2)
cat("\nAnOVa to compare models\n");  anova(lme.base,lme.base.het1,lme.base.het2)
```

So heterogeneous 2 model (by Site) is a statistically better fit than heterogeneous 1 model (by Drain) = variation at *Site* level.

**Industrial proportion** is statistically significant -- *positive* relationship.

<hr>

# REGRESSION on NATURAL PROPORTION
(sum of water environment and natural environment)

## basic prediction of MP using proportion of natural land

```{r MP using proportion of natural, paged.print=FALSE}
lme.base <- lme(count_corr_across_sizes.L ~ natural, 
                control = ctrl,
                random = ~1|Site, 
                data = cassie)  
summary(lme.base)
```

So ungrouped proportion natural has no effect on MP count.

## Prediction of MP by proportion natural varying by Drain

```{r MP by proportion natural varying by Drain, paged.print=F}
lme.base.het1 <- lme(count_corr_across_sizes.L ~ natural, 
                     weights = varIdent(form = ~1 | Drain), 
                     control = ctrl,
                     random = ~1|Site, 
                     data = cassie)  
summary(lme.base.het1)
cat("\nAnOVa to compare models\n");  anova(lme.base,lme.base.het1)
```

Lower AIC and low p-value say heterogeneous model a better fit

## Prediction of MP by proportion natural, varying by Site

```{r MP on natural and Site, paged.print=F}
lme.base.het2 <- lme(count_corr_across_sizes.L ~ natural, 
                     weights = varIdent(form = ~1 | Site), 
                     control = ctrl,
                     random = ~1|Site, 
                     data = cassie)  
summary(lme.base.het2)
cat("\nAnOVa to compare models\n");  anova(lme.base,lme.base.het1,lme.base.het2)
```

So heterogeneous 2 model (by Site) is a statistically better fit than heterogeneous 1 model (by Drain) = variation at *Site* level.

**Natural land-use proportion** has statistically significant effect on MP counts -- *positive* relationship.

<hr>

# REGRESSION on  SERVICES PROPORTION

## basic prediction of MP using proportion of services land

```{r MP sefvices ungrouped, paged.print=FALSE}
lme.base <- lme(count_corr_across_sizes.L ~ services, 
                control = ctrl,
                random = ~1|Site, 
                data = cassie)  
summary(lme.base)
```

So ungrouped proportion services has no effect on MP count.

## Prediction of MP by proportion Services varying by Drain

```{r MP services Drain, paged.print=FALSE}
lme.base.het1 <- lme(count_corr_across_sizes.L ~ services, 
                     weights = varIdent(form = ~1 | Drain), 
                     control = ctrl,
                     random = ~1|Site, 
                     data = cassie)  
summary(lme.base.het1)
cat("\nAnOVa to compare models\n");  anova(lme.base,lme.base.het1)
```

There is a *significant effect of service land-use proportion*. Lower AIC and low p-value mean the heterogeneous model (by Drain) is a better fit.

## Prediction of MP by proportion services, varying by Site

```{r MP services Site, paged.print=FALSE}
lme.base.het2 <- lme(count_corr_across_sizes.L ~ services, 
                     weights = varIdent(form = ~1 | Site), 
                     control = ctrl,
                     random = ~1|Site,
                     data = cassie)  
summary(lme.base.het2)
cat("\nAnOVa to compare models\n"); anova(lme.base,lme.base.het1,lme.base.het2)
```

So based on lower AIC and p<0.05, heterogeneous 2 model (by Site) is a statistically better fit than heterogeneous 1 model (by Drain) = variation at *Site* level.

**Services land-use proportion** has statistically significant effect on MP counts -- *positive* relationship.

<hr>

# REGRESSION on PUBLIC OPEN SPACE PROPORTION

## basic prediction of MP using proportion of public open space land

```{r public open ungrouped, paged.print=F}
lme.base <- lme(count_corr_across_sizes.L ~ public_open, 
                control = ctrl,
                random = ~1|Site, 
                data = cassie)  
summary(lme.base)
```

So ungrouped proportion public_open has no effect on MP count.

## Prediction of MP by proportion public open space, varying by Drain

```{r public open var by Drain, paged.print=F}
lme.base.het1 <- lme(count_corr_across_sizes.L ~ public_open, 
                     weights = varIdent(form = ~1 | Drain), 
                     control = ctrl,
                     random = ~1|Site, 
                     data = cassie)  
summary(lme.base.het1)
cat("\nAnOVa to compare models\n");  anova(lme.base,lme.base.het1)
```

There is a *significant effect of public open space land-use proportion*. Lower AIC and low p-value mean the heterogeneous model (by Drain) is a better fit.

## Prediction of MP by proportion services, varying by Site

```{r POS var by Site, paged.print=F}
lme.base.het2 <- lme(count_corr_across_sizes.L ~ public_open, 
                     weights = varIdent(form = ~1 | Site), 
                     control = ctrl,
                     random = ~1|Site, 
                     data = cassie)  
summary(lme.base.het2)
cat("\nAnOVa to compare models\n"); anova(lme.base,lme.base.het1,lme.base.het2)
```

So based on lower AIC and p<0.05, heterogeneous 2 model (by Site) is a statistically better fit than heterogeneous 1 model (by Drain) = variation at *Site* level.

**Public open space land-use proportion** has statistically significant effect on MP counts -- *positive* relationship.

<hr>=-=-=-=-=-=-

# What if linear relationship not found

use this section of code if you need to explore other options

<hr>=-=-=-=-=-=-

*exploration of log(Y) is something you can look at.  Note anova() cant be used to compare log(Y)~ models and Y~ models*

```{r}
lme.base.het2.log <- lme(log(count_corr_across_sizes.L) ~
                           catchment_pop, weights = varIdent(form = ~1 | Site), control = ctrl,
                         random = ~1|Site, data = cassie)  
summary(lme.base.het2.log)
```

Looking for nonlinear effect
```{r}
lme.base.het2.quad <- lme(count_corr_across_sizes.L ~
                            catchment_pop + I(catchment_pop^2), weights = varIdent(form = ~1 | Site), control = ctrl,
                          random = ~1|Site, data = cassie)  
summary(lme.base.het2.quad)
```

so maybe something here:  hard to see

so lets scale so we can see what is happening
```{r}
cassie$pop <-cassie$catchment_pop/1000 # scale up by 1E3

lme.base.het2.quad2 <- 
  lme(count_corr_across_sizes.L ~ pop + I(pop^2), 
      weights = varIdent(form = ~1 | Site), 
      control = ctrl,
      random = ~1|Site, 
      data = cassie)  
summary(lme.base.het2.quad2)
```

can solve for the turning point (quadratic and see)

#maybe impose cubic
```{r}
lme.base.het2.cub <- 
  lme(count_corr_across_sizes.L ~ I(catchment_pop^3), 
      weights = varIdent(form = ~1 | Site), 
      control = ctrl,
      random = ~1|Site,
      data = cassie)  
summary(lme.base.het2.cub)
```

#Hmmmmmmmm
so look closely at the quadratic maybe runs the other way

```{r}
summary(lme.base.het2.quad2)
```

a log on x would capture this, approximately
```{r}
lme.base.het2.xlog <- 
  lme(count_corr_across_sizes.L ~ log(catchment_pop), 
      weights = varIdent(form = ~1 | Site), 
      control = ctrl,
      random = ~1|Site, 
      data = cassie)  
summary(lme.base.het2.xlog)
```

so maybe there is a population effect ...
this is showing whether variance is constant - HINT it is not, 
therefore use heterogeneous

```{r}
summary(lme.base.het2$modelStruct$varStruct)
summary(lme.base.het1$modelStruct$varStruct)
```

*lots to explore*

<hr>
