---
title: "Cassie plots"
documentclass: article
classoption: a4paper
output: word_document
fig_height: 50%
fig_width: 50%
geometry: margin=0.6in
---

# Cassie Bond - Plots for microplastics data

```{r read data if needed, eval=FALSE, message=FALSE, warning=FALSE, include=FALSE}
setwd("C:/Users/00028958/LocalData/R Projects/Cassie_Bond/")
cassie <- read.csv("cassie.csv" , stringsAsFactors = T)
summary(cassie)
str(cassie)
allsizes <- read.csv("cassie_allsizes.csv")
allsizes$Drain <- as.factor(allsizes$Drain)
allsizes$Site <- as.factor(allsizes$Site)
allsizes$Rep.fac <- as.factor(allsizes$Rep)
allsizes$Size.fac <- cut(allsizes$Size, breaks = c(seq(0.5,4.5,1)), 
                         labels = c("530 µm","190 µm","100 µm","25 µm"))
```

```{r load packages etc, echo=-1, message=FALSE, warning=FALSE}
load("C:/Users/00028958/LocalData/R Projects/Cassie_Bond/.Rdata")
library(nlme)
library(multcomp)
library(car)
```

## Boxplots comparing microplastic conentrations by Drain and Site

```{r box plot MP by Drain and Site, fig.cap="Comparison of microplastic concentrations (a) in each catchment and (b) at each site.", fig.height=8, fig.width=7}
par(mar = c(0,0,0,0), oma = c(4,12,1,1), mgp = c(2,0.3,0), tcl = 0.3, font.lab = 2,
    lend="square", ljoin = "mitre", xpd=T)
palette(c("black",colorRampPalette(c("#FFE6A3", "#B1609F", "#5560A4"))(6)))
layout(matrix(c(1,2,2), ncol=1))
with(cassie, boxplot(counts_corr_perL ~ Drain, xlim=c(6.65,0.35),
                     horizontal = T, las = 1, xaxt="n", cex = 1.6, 
                     col=seq(2,7), cex.lab = 1.5, cex.axis = 1.2,
                     xlab="", yaxt="n"))
axis(2, las = 2, cex.axis = 1.6, at = seq(1,6,1),
     labels = c("Bayswater","Claisebrook","Kitchener",
                "Osborne Park","South Belmont", "South Coolup"))
mtext("Drain Catchment",2,9.5,font=2,cex=1.2)
text(11.5,0.65,labels="(a)", font = 2, cex = 2)
axis(1, labels=NA, tcl = 0.3)
axis(1, labels=NA, tcl = -0.3)
with(cassie, boxplot(counts_corr_perL ~ Site, xlim=c(12.65,0.35),
                     horizontal = T, las = 1, cex = 1.6, 
                     col=rep(seq(2,7), each=2), cex.lab = 1.5, cex.axis = 1.6,
                     xlab=""))
mtext("Microplastic counts (particles/L)",1,2,font=2, cex = 1.2)
mtext("Sampling Site",2,4,font=2,cex=1.2)
text(11.5,0.4,labels="(b)", font = 2, cex = 2)
```

```{r reset graphics layout, message=FALSE, warning=FALSE, include=FALSE}
layout(matrix(c(1), ncol=1))
```

## Percentage bar plot for microplastic morphology

```{r bar plot by shape, fig.align='center', fig.cap="Proportions of microplastics of different morphologies for the different drain catchments.", fig.height=3.6, fig.width=8}
ByMorph1 <- aggregate(cassie[,c(7,9,11,15)], by=list(cassie$Drain), FUN = mean)
ByMorph2 <- apply(ByMorph1[,2:5], MARGIN = 1, FUN = function(x){100*x/sum(x)})
colnames(ByMorph2) <- as.character(ByMorph1[,1]) ; rm(ByMorph1)
par(mar = c(3,8,1,8), mgp=c(1.6,0.3,0), tcl = 0.3, font.lab = 2, cex.lab = 1.2,
    lend="square", ljoin = "mitre", xpd = TRUE)
barplot(ByMorph2, horiz = T, las=1, xlab = "Proportion (%)", 
        col = colorRampPalette(c("sienna","wheat"))(4), 
        names.arg = c("Bayswater","Claisebrook","Kitchener","Osborne Park",
                      "South Belmont","South Coolup"))
mtext("Drain catchment", 2, 6.8, font = 2, cex = 1.3)
legend(102, 6, bty = "n", cex = 1.2, pch = 22, 
       pt.bg = colorRampPalette(c("sienna","wheat"))(4),
       legend = c("Fragment","Film","Bead","Fibre"), pt.cex = 4,
       title = expression(bold("Morphology")), 
       x.intersp = 1.5, y.intersp = 1.5)
```

## Percentage bar plot for microplastic size

```{r bar plot by size, fig.align='center', fig.cap="Proportions of microplastics of different particle sizes for the different drain catchments.", fig.height=3.6, fig.width=8, paged.print=FALSE}
BySize1 <- aggregate(allsizes$corrected.counts.perL, 
                   by=list(allsizes$Size.fac, allsizes$Drain), FUN = mean)
BySize2 <- matrix(BySize1$x, ncol = 6, byrow=FALSE)
colnames(BySize2) <- levels(allsizes$Drain)
rownames(BySize2) <- levels(allsizes$Size.fac)
BySize3 <- apply(BySize2, MARGIN = 2, FUN = function(x){100*x/sum(x)})
par(mar = c(3,8,1,8), mgp=c(1.6,0.3,0), tcl = 0.3, font.lab = 2, cex.lab = 1.2,
    lend="square", ljoin = "mitre", xpd = TRUE)
barplot(BySize3, horiz = T,  las=1, xlab = "Proportion (%)", 
        col = colorRampPalette(c("#003087","#C5C7EA"))(4), 
        names.arg = c("Bayswater","Claisebrook","Kitchener","Osborne Park",
                      "South Belmont","South Coolup"))
mtext("Drain catchment", 2, 6.8, font = 2, cex = 1.3)
legend(102, 6, bty = "n", cex = 1.2, pch = 22, 
       pt.bg = colorRampPalette(c("#003087","#C5C7EA"))(4),
       legend = row.names(BySize3), pt.cex = 4,
       title = expression(bold("Size")), 
       x.intersp = 1.5, y.intersp = 1.5)
rm(list = c("BySize1","BySize2"))
```

## Percentage bar plot for microplastic colour

```{r bar plot by colour, fig.align='center', fig.cap="Proportions of microplastics of different colours for the different drain catchments.", fig.height=3.6, fig.width=8}
MPcols <- read.table(file="MPcols.csv", sep=",", row.names = 1, header = T)
MPpal <- c("red", "salmon", "gray75", "mediumseagreen", "ivory", "burlywood3", 
           "dodgerblue", "gray10") ; palette(c("black",MPpal))
par(mar = c(3,8,1,8), mgp=c(1.6,0.3,0), tcl = 0.3, font.lab = 2, cex.lab = 1.2,
    lend="square", ljoin = "mitre", xpd = TRUE)
barplot(t(as.matrix(MPcols)), horiz = T, 
        col = 2:9, las=1, 
        names.arg = c("Bayswater","Claisebrook","Kitchener","Osborne Park",
                      "South Belmont","South Coolup"),
        xlab = "Proportion (%)")
mtext("Drain catchment", 2, 6.8, font = 2, cex = 1.3)
legend(102, 7, bty = "n", cex = 1.1, pch = 22, pt.cex = 3.6, 
       pt.bg = 2:9, legend = colnames(MPcols),
       title = expression(bold("Colour")), 
       x.intersp = 1.5, y.intersp = 1.4)
```

<hr>

## Percentage bar plots for microplastic morphology, size, and colour

```{r bar plots by shape size colour, fig.align='center', fig.cap="Proportions of microplastics of different (a) morphologies, (b) sizes, and (c) colours, for the different drain catchments.", fig.height=9, fig.width=7}
par(mfrow = c(3,1), oma = c(4,0,2,0), mar = c(0,10.5,0,11), mgp=c(1.6,0.2,0), 
    tcl = 0.3, font.lab = 2, cex.lab = 1.2, cex.axis = 1.4, 
    xpd = TRUE, lend="square", ljoin = "mitre")
barplot(ByMorph2, horiz = T, las=1, xlab = "",xaxt="n", 
        col = colorRampPalette(c("sienna","wheat"))(4), 
        names.arg = c("Bayswater","Claisebrook","Kitchener","Osborne Park",
                      "South Belmont","South Coolup"))
axis(3, cex.axis = 1.4)
mtext("Drain catchment", 2, 8.5, font = 2, cex = 1.1)
legend(102, 6.5, bty = "n", cex = 1.4, pch = 22, 
       pt.bg = colorRampPalette(c("sienna","wheat"))(4),
       legend = c("Fragment","Film","Bead","Fibre"), pt.cex = 4,
       title = expression(bold("(a)\nMorphology")), title.cex = 1.6, 
       x.intersp = 1.5, y.intersp = 1.5)
# -=-=-=-=-=-=-=-=-=-
barplot(BySize3, horiz = T,  las=1, xlab = "", xaxt="n", 
        col = colorRampPalette(c("#003087","#C5C7EA"))(4), 
        names.arg = c("Bayswater","Claisebrook","Kitchener","Osborne Park",
                      "South Belmont","South Coolup"))
mtext("Drain catchment", 2, 8.5, font = 2, cex = 1.1)
legend(102, 6.5, bty = "n", cex = 1.4, pch = 22, 
       pt.bg = colorRampPalette(c("#003087","#C5C7EA"))(4),
       legend = row.names(BySize3), pt.cex = 4,
       title = expression(bold("(b)\nMinimum size")), title.cex = 1.6, 
       x.intersp = 1.5, y.intersp = 1.5)
# -=-=-=-=-=-=-=-=-=-
barplot(t(as.matrix(MPcols)), horiz = T, 
        col = 2:9, las=1, 
        names.arg = c("Bayswater","Claisebrook","Kitchener","Osborne Park",
                      "South Belmont","South Coolup"))
mtext("Drain catchment", 2, 8.5, font = 2, cex = 1.1)
legend(102, 6.5, bty = "n", cex = 1.4, pch = 22, pt.cex = 4, 
       pt.bg = 2:9, legend = c("red","orange-pink","grey","green","white-clear",
                               "brown","blue","black"),
       title = expression(bold("(c)\nPolymer color")), 
       x.intersp = 1.4, y.intersp = 1.3, title.cex = 1.6)
mtext("Proportion (%)",1,2,cex = 1.1, font = 2)
```

## Raman spectra for microplastics and natural polymers

```{r Raman spectra, fig.height=8, fig.width=7, fig.align='center', fig.cap="Raman spectra for the synthetic (a -- d) and natural (e -- f) polymer types identified in microplastics samples.", results='hold'}
par(mfrow = c(6,1), mar = c(0,6,0,1), oma = c(4,0,2,0), mgp = c(4, 0.4, 0),
    tcl = 0.2, lend = 0, ljoin = 0, font.lab = 2, xpd=TRUE, cex.lab = 1.4, las=1,
    cex.axis = 1.4)
palette(c("black",colorRampPalette(c("#93721A", "#A51890", "#5560A4"))(6)))
#  -=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-
with(K_PP, plot(V2 ~ V1, type = "l", col = 7,
                xaxt = "n", cex.axis=1.4,
                ylab = "", xlim = c(0,3150)))
axis(1, labels=F);axis(3)
mtext("(a) Polypropylene (PP)", side = 3, line = -1.5, adj = 0.7, col = 7)
#  -=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-
with(SC_PE, plot(V2 ~ V1, type = "l", col = 6,
                 xaxt = "n", xlab = "", cex.axis=1.4,
                 ylab = "", xlim = c(0,3150)))
mtext("(b) Polyethylene (PE)", side = 3, line = -1.5, adj = 0.7, col = 6)
#  -=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-
with(H_PTFE, plot(V2 ~ V1, type = "l", col = 5,
                  xaxt = "n", yaxt = "n", xlab="",
                  ylab = "", xlim = c(0,3150), ylim = c(0,5500)))
rect(-20,5000,100,par("usr")[4],lwd=0.01, border="white",col="white");box()
with(H_PTFE, lines(V2~V1, col = 3, lty=3))
axis(1, labels=F)
axis(2, at=c(0,2000,4000), labels=c(0,2000,4000), cex.axis=1.4)
mtext("(c) Polytetrafluoroethylene (PTFE)", side = 3,line = -1.5,adj = 0.7,col = 5)
#  -=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-
with(SB_PVDF, plot(V2 ~ V1, type = "l", col = 4,
                   xaxt = "n", cex.axis=1.4,
                   ylab = "", xlim = c(0,3150)))
axis(1, labels=F)
mtext("(d) Polyvinylidene fluoride (PVDF)", side = 3, line = -1.5, adj = 0.7,col=4)
mtext("Intensity", 2, 3, cex = 1.2, adj=1, font=2, las=0)
#  -=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-
with(H_Cotton, plot(V2 ~ V1, type = "l", col = 3,
                    xaxt = "n",yaxt = "n",
                    ylab = "", xlim = c(0,3150), ylim = c(0,5500)))
rect(-20, 5000, 100, par("usr")[4], lwd=0.01, border="white", col="white");box()
with(H_Cotton, lines(V2~V1, col = 2, lty=3))
axis(1, labels=F)
axis(2, at=c(0,2000,4000), labels=c(0,2000,4000), cex.axis=1.4)
mtext("(e) Cotton", side = 3, line = -1.5, adj = 0.7, col = 3)
#  -=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-
with(K_Wool, plot(V2 ~ V1, type = "l", col = 2,
                  yaxt="n",
                  ylab = "", xlim = c(0,3150)))
axis(1, labels=F)
axis(2, at=c(0,200,400), labels=c(0,200,400), cex.axis=1.4)
mtext("(f) Wool", side = 3, line = -1.5, adj = 0.7, col = 2)
mtext(expression(bold(paste("Relative wavenumbers (",cm^"-1",")"))), 1, 2.2)
#  -=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-
```
